### 2020-09-15 paper/appendA.tex
Style fixes

\section{Introduction}
\TODO{some intro}

@@

\begin{defnTwo}[good partition]
  A \emph{good partition} of a graph $G$ is a partition $(K_1, K_2, K_3, L, R)$ of $V(G)$ such that:
  \begin{itemize}
    \item $L$ and $R$ are not empty, and $L$ is anticomplete to $R$,
    \item $K_1 \cup K_2$ and $K_2 \cup K_3$ are cliques,
    \item in the graph obtained from $G$ by removing all edges between $K_1$ and $K_3$, every chordless path with one end in $K_1$, the other in $K_3$, and interior in $L$ contains a vertex from $L$ that is complete to $K_1$,
    \item either $K_1$ is anticomplete to $K_3$, or no vertex in $L$ has neighbors in both $K_1$ and $K_3$,
    \item for some $x \in L$ and $y \in R$, there is a triad of $G$ that contains $\{x, y\}$.
  \end{itemize}
\end{defnTwo}

\TODO{we need many more definitions, scan pseudocode}

@@

@@

\begin{itemize}
	\item $a \gets b$ -- let a be equal b.
	\item $a :\in X$, when $X$ is a set -- let a be equal to any element of $X$
	\item $a \xor b$, when $a$ and $b$ are logical values -- $a$ xor $b$
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious.
	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors.
	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors.
	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$.
	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$.
	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$.
	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$.
	\item $[n]$  -- $\{1, \ldots, n\}$.
	\item \LGBSK -- the line-graph of a biparite subdivision of $K_4$.

	\item Strip $S_{uv}$ is \emph{rich} if and only if $S_{uv} \setminus T_{uv} \neq \emptyset$
\end{itemize}
\TODO{Introduction on unknown structures - J-strip etc etc}

\section{Algorithms}

\graphAppendix{Color square-free perfect graph}
\input{coloringAppendix/algI.tex}
\clearpage

\graphAppendix{Color good partition}
\input{coloringAppendix/algII.tex}
\clearpage

\graphAppendix{Grow hyperprism}
\input{coloringAppendix/algIII.tex}
\clearpage

\graphAppendix{Good partition from an even hyperprism}
\input{coloringAppendix/algIV.tex}
\clearpage

\graphAppendix{Good partition from an odd hyperprism}
\input{coloringAppendix/algV.tex}
\clearpage

\graphAppendix{Good partition from a $J$-strip system}
\input{coloringAppendix/algVIa.tex}
\clearpage

\graphAppendix{Good partition from a special $K_4$ strip system}
\input{coloringAppendix/algVIb.tex}
\clearpage

\graphAppendix{Find a special $K_4$ system}
\input{coloringAppendix/algVII.tex}
\clearpage

\graphAppendix{Growing a $J$-strip}
\input{coloringAppendix/algVIII.tex}
\clearpage

% \graphAppendix{LAST}
% \input{coloringAppendix/algIXa.tex}
% \clearpage

>>>>

\section{Introduction}
\TODO{some intro}
We give a brief overview of the square-free perfect graph coloring algorithm and a pseudocode thereof. The work is not intended to be self-contained and will be impossible to fully understand without \cite{coloringSquareFree} at hand. But when reading \cite{coloringSquareFree}, one may pose a question of what sort of an algorithm emerges from it, and we believe the pseudocode below gives a first overview and is a major step required before an attempt to implement it would be made. For some, looking at the pseudocode could provide a better way to analyze and possibly simplify the algorithm.

What we present would not be trivial to implement. For example in many places we say ''choose $x$, so that \dots'', without specifying how to do it. A most glaring example is calculating an inverse of a line graph (in \Cref{alg:growingJStrip}) which is a complicated algorithm in and of itself, see \cite{Liu2014} for reference.

@@

\begin{defnTwo}[good partition]
  A \emph{good partition} of a graph $G$ is a partition $(K_1, K_2, K_3, L, R)$ of $V(G)$ such that:
  \begin{itemize}
    \item $L$ and $R$ are not empty, and $L$ is anticomplete to $R$,
    \item $K_1 \cup K_2$ and $K_2 \cup K_3$ are cliques,
    \item in the graph obtained from $G$ by removing all edges between $K_1$ and $K_3$, every path with one end in $K_1$, the other in $K_3$, and interior in $L$ contains a vertex from $L$ that is complete to $K_1$,
    \item either $K_1$ is anticomplete to $K_3$, or no vertex in $L$ has neighbors in both $K_1$ and $K_3$,
    \item for some $x \in L$ and $y \in R$, there is a triad of $G$ that contains $\{x, y\}$.
  \end{itemize}
\end{defnTwo}

@@

A few more structures are used throughout the algorithm. Let us define them.

For definitions \ref{def:majorNeiOfPrism} and \ref{def:localSubOfPrism}, let $K$ be a prism with triangles $\{a_1, a_2, a_3\}$ and $\{b_1, b_2, b_3\}$ and with paths $R_1, R_2, R_3$, where each $R_i$ has ends $a_i$ and $b_1$.

\begin{defnTwo}[major neighbor of a prism]
  A vertex $v \in V(G) \setminus K$ is a \emph{major neighbor} of pritm $K$ is and only if it has at least two neighbors in $\{a_1, a_2, a_3\}$ and at least two neighbors in $\{b_1, b_2, b_3\}$.
  \label{def:majorNeiOfPrism}
\end{defnTwo}

\begin{defnTwo}[local subset of a prism]
  A subset $X \subseteq V(K)$ is \emph{local} if either $X \subseteq \{a_1, a_2, a_3\}$, or $X \subseteq \{b_1, b_2, b_3\}$, or $X \subseteq R_i$ for some $i \in \{1, 2, 3\}$.
  \label{def:localSubOfPrism}
\end{defnTwo}

\begin{defnTwo}[attachment]
  Let $F, K$ be an induced subgraphs of a graph $G$, with $V(F) \cap V(K) = \emptyset$. Any vertex $k \in V(K)$ that has a neighbor in $V(F)$ in a graph $G$ is called an \emph{attachment} of $F$ in $K$. Whenever any vertex $k \in V(K)$ has an attachment of $F$ we say that $F$ \emph{attaches} to $K$.
\end{defnTwo}

\begin{defnTwo}[hyperprism]
  A \emph{hyperprism} is a graph $H$, whose vertices can be partitioned into nine sets:
  $$
  \begin{tabular}{c c c}
    $A_1$ & $C_1$ & $B_1$ \\
    $A_2$ & $C_2$ & $B_2$ \\
    $A_3$ & $C_3$ & $B_3$
  \end{tabular}
  $$
  \noindent with the following properties:
  \begin{itemize}
    \item each of $A_1, A_2, A_3, B_1, B_2, B_3$ is nonempty,
    \item for distinct $i, j \in \{1, 2, 3\}$, $A_i$ is complete to $A_j$, and $B_i$ is complete to $B_j$, and there are no other edges between $A_i \cup B_i \cup C_i$ and $A_j \cup B_j \cup C_j$,
    \item for each $i \in \{1, 2, 3\}$, every vertex of $A_i \cup B_i \cup C_i$ belongs to a path between $A_i$ and $B_i$ with interior in $C_i$.
  \end{itemize}
\end{defnTwo}

Whenever we will speak about hyperprisms, we will denote its subsets as in the above definition, unless stated otherwise.

For a hyperprism $H$ we have a few more definitions:

\begin{defnTwo}[$i$-rung of a hyperprism]
  For each $i \in \{1, 2, 3\}$, any path from $A_i$ to $B_i$ with interior in $C_i$ is called an \emph{$i$-rung}.
\end{defnTwo}

\begin{defnTwo}[strip of a hyperprism]
  For each $i \in \{1, 2, 3\}$, the triple $(A_i, C_i, B_i)$ is called a \emph{strip} of the hyperprism.
\end{defnTwo}

\begin{defnTwo}[instance of a hyperprism]
  For each $i \in \{1, 2, 3\}$, let us pick any $i$-rung $R_i$. Then $R_1$, $R_2$, $R_3$ form a prism. Any such prism is called an \emph{instance} of a hyperprism.
\end{defnTwo}

From the definition of an instance of a hyperprism, we can see that any prism is also a hyperprism.

Let us note, that if a hyperprism $H$ contains no odd hole, all rungs have the same parity. We then call the hyperprism odd or even accordingly.

Given a graph $G$ that contains a hyperprism $H$, we can define a few more structures.

\begin{defnTwo}[major neighbor of a hyperprism]
  A vertex $v \in V(G) \setminus V(H)$ is a \emph{major neighbor} of $H$, if it is a major neighbor of some instance of $H$.
\end{defnTwo}

\begin{defnTwo}[local subset of a hyperprism]
  A subset $X \subseteq V(H)$ is a local subset of a hyperprism $H$ if either $X \subseteq A_i \cup A_2 \cup A_3$ or $X \subseteq B_1 \cup B_2 \cup B_3$ or $X \subseteq A_i \cup B_i \cup C_i$ for some $i \in \{1, 2, 3\}$.
\end{defnTwo}

\begin{defnTwo}[maximal hyperprism]
  A hyperprism $H$ is \emph{maximal} if there is no hyperprism $H'$ in $G$, such that $V(H) \varsubsetneq V(H')$.
\end{defnTwo}

\Cref{alg:growHyperprism} for growing hyperprism is based upon the following theorem. Recall that by $K_4$ we denote a clique on 4 vertices.
\begin{theorem}[Lemma 3.3 of \cite{coloringSquareFree}]
  Let $G$ be a berge graph, let $H$ be a hyperprism in $G$ and let $M$ be the set of major neighbors of $H$ in $G$. Let $F$ be a component of $V(G) \setminus(V(H) \cup M)$, such that the set of attachments of $F$ in $H$ is not local. Then one can find in polynomial time one of the following
  \begin{itemize}
    \item a path $P$, with $\emptyset \neq V(P) \subseteq V(F)$, such that $V(H) \cup V(P)$ induces a hyperprism,
    \item a path $P$, with $\emptyset \neq V(P) \subseteq V(F)$, and for each $i \in \{1, 2, 3\}$ an $i$-rung $R_i$ of $H$, such that $V(P) \cup V(R_1) \cup V(R_2) \cup V(R_3)$ induces the line graph of a bipartite subdivision of $K_4$.
  \end{itemize}
  \label{thm:growingHyperprism}
\end{theorem}

If at any time during growing a hyperprism we encounter the latter outcome of the \Cref{thm:growingHyperprism} we stop it and instead focus on the newly found line graph of a bipartite subdivision of $K_4$. Algorithms \ref{alg:goodPartitionJStrip}, \ref{alg:goodPartitionSpecialK4}, \ref{alg:findSpecialK4} and \ref{alg:growingJStrip} take their roots in the following theorem.

\begin{theorem}[Theorem 6.1 of \cite{coloringSquareFree}]
  Let $G$ be a square-free Berge graph, and assume that $G$ contains the line graph of a bipartite subdivision of $K_4$. Then $G$ admits a good partition.
\end{theorem}

Before providing the pseudocode, we need a few more definitions.

\begin{defnTwo}[branch]
  Given a graph $G$, a \emph{branch} is a path whose interior vertices have degree 2 and whose ends have degree at leas 3. A \emph{branch-vertex} is any vertex of degree at least 3.
\end{defnTwo}

\begin{defnTwo}[appearance of a graph]
  Given a graph $G$, and \emph{appearance} of a graph $J$ is any induced subgraph of $G$ that is isomorphic to the line graph $L(H)$ of a bipartite subdivision $H$ of $J$. An appearance of $J$ is \emph{degenerate} if either $J = H = K_{3, 3}$\footnote{$K_{n, m}$ is a complete bipartite graph with $n$ vertices on the one side and $m$ vertices on the other}, or $J = K_4$ and the four vertices of $J$ form a square in $H$.
\end{defnTwo}

Note that a degenerate appearance of a graph contains a square.

\begin{defnTwo}[overshadowed appearance]
  An appearance of $L(H)$ of $J$ in $G$ is \emph{overshadowed} if there is a branch $B$ of $H$, of length at least 3, with ends $b_1, b_2$, such that some vertex of $G$ is non-adjacent in $G$ to at most one vertex in $\{b_1x \in V(L(H))$, for $x \in V(H), b_1x \in E(H)\}$ and at most one vertex in $\{b_2x \in V(L(H))$, for $x \in V(H), b_2x \in E(H)\}$.
\end{defnTwo}

\begin{defnTwo}[$J$-enlargement]
  An \emph{enlargement} of a 3-connected graph $J$, or a $J$-enlargement is any 3-connected graph $J'$ such that there is a proper induced subgraph of $J'$ that is isomorphic to a subdivision of $J$.
\end{defnTwo}

\begin{defnTwo}[$J$-strip system, $uv$-rung]
  Let $J$ be a 3-connected graph and let $G$ be a perfect graph. A \emph{$J$-strip system} $(S, N)$ in $G$ means
  \begin{itemize}
    \item for each edge $uv$ of $J$, a subset $S_{uv} = S_{vu}$ of $V(G)$,
    \item for each vertex $v$ of $J$, s subset $N_v$ of $V(G)$,
    \item $N_{uv} = S_{uv} \cap N_u$,
  \end{itemize}
  such that if we define a $uv$-rung to be a path $R$ of $G$ with ends $s, t$, where $V(R) \subseteq S_{uv}$, and $s$ is the unique vertex of $R$ in $N_u$, and $t$ is the unique vertex of $R$ in $N_v$, the following conditions are met:
  \begin{itemize}
    \item the sets $S_{uv}$, for $uv \in E(J)$ are pairwise disjoint,
    \item for each $u \in V(J)$, $N_u \subseteq \bigcup_{uv \in E(J)} S_{uv}$,
    \item for each $uv \in E(J)$, every vertex of $S_{uv}$ is in a $uv$-rung,
    \item for any two edges $uv, wx$ of $J$, with $u, v, w, x$ all distinct, there are no edges between $S_{uv}$ and $S_{wx}$,
    \item if $uv, uw \in E(J)$, with $v \neq w$, then $N_{uv}$ is complete to $N_{uw}$ and there are no other edges between $S_{uv}$ and $S_{uw}$,
    \item for each $uv \in E(J)$, there is a \emph{special} $uv$-rung, such that for every cycle $C$ of $J$, the sum of the lengths of the special $uv$-rungs for $uv \in E(C)$ has the same parity as $|V(C)|$.
  \end{itemize}
\end{defnTwo}

\noindent The vertex set of $(S, N)$, denoted by $V(S, N)$ is the set $\bigcup_{uv \in E(J)} S_{uv}$. Note that in general $N_{uv}$ is different from $N_{vu}$. On the other hand $S_{uv} = S_{vu}$.

A $J$-strip system has the following properties:
\begin{itemize}
  \item for distinct $u, v \in V(J)$, if $uv \in E(J)$, then $N_u \cap N_v \subseteq S_{uv}$ and if $uv \notin E(J)$ then $N_u \cap N_v = \emptyset$,
  \item for $uv \in E(J)$ and $w \in V(J)$, if $w \neq u$ then $S_{uv} \cap N_w = \emptyset$,
  \item for every $uv \in E(J)$, all $uv$-rungs have lengths of the same parity,
  \item for every cycle $C$ of $J$ and every choice of $uv$-rung for every $uv \in E(C)$, the sums of the lengths of the $uv$-rungs have the same parity as $|V(C)|$. In particular, for each edge $uv \in E(J)$, all $uv$-rungs have the same parity.
\end{itemize}

\begin{defnTwo}[choice of rungs]
  Given a $J$-strip system, by a \emph{choice of rungs} we mean the choice of one $uv$-rung for each edge $uv$ of $J$.
\end{defnTwo}

Given a square-free perfect graph $G$ and a $J$-strip system, for every choice of rungs, the subgraph of $G$ induced by their union is the line-graph of a bipartite subdivision of $J$.

\begin{defnTwo}[saturating $J$-strip system]
  $X \subseteq V(G)$ \emph{saturates} the strip system if for every $u \in V(J)$ there is at most one neighbor $v$ of $u$ such that $N_{uv} \nsubseteq X$.
\end{defnTwo}

\begin{defnTwo}[major vertex w.r.t. a strip system]
  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) the strip system if the set of its neighbors saturates the strip system.
\end{defnTwo}

\begin{defnTwo}[major vertex w.r.t. some choice of rungs]
  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) some choice of rungs if the $J$-strip system defined by this choice of rungs is saturated by the set of neighbors of $v$.
\end{defnTwo}

\begin{defnTwo}[subset local w.r.t. a strip system]
  A subset $X \subseteq V(S, N)$ is \emph{local} with respect to (w.r.t.) the strip system, if either $X \subseteq N_v$ for some $v \in V(J)$ or $X \subseteq S_{uv}$ for some $uv \in E(J)$.
\end{defnTwo}

The outline of the algorithm is as follows. Given a square-free perfect graph, first we test if it is an Artemis graph. If so, we color it according to \Cref{thm:colorArtemis}. If not, \Cref{thm:getPrism} gives us a prism $K$. We want to extend $K$ either to a maximal hyperprism or to the line graph of a bipartite subdivision of $K_4$. For each of them, we can construct a good partition, which we color recursively.

@@

\begin{itemize}
	\item $a :\in X$, when $X$ is a set -- let a be equal to any element of $X$,
	\item $a \xor b$, when $a$ and $b$ are logical values -- $a$ xor $b$,
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious,
	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors,
	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors,
	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$,
	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$,
	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$,
	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$,
	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$,
	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$,
	\item $[n]$  -- $\{1, \ldots, n\}$,
	\item \LGBSK -- the line-graph of a biparite subdivision of $K_4$.
\end{itemize}

Also, throughout the algorithms, we have many lines with asserts. These check some of the properties required before proceeding, and should all be true.

\clearpage
\section{Algorithms}

\graphAppendix{Color square-free perfect graph}{alg:colorSquareFree}
\input{coloringAppendix/algI.tex}
\clearpage

\graphAppendix{Color good partition}{alg:colorGoodPartition}
\noindent\input{coloringAppendix/algII.tex}
\clearpage

\graphAppendix{Grow hyperprism}{alg:growHyperprism}
\noindent\input{coloringAppendix/algIII.tex}
\clearpage

\graphAppendix{Good partition from an even hyperprism}{alg:goodPartitionEvenH}
\input{coloringAppendix/algIV.tex}
\clearpage

\graphAppendix{Good partition from an odd hyperprism}{alg:goodPartitionOddH}
\input{coloringAppendix/algV.tex}
\clearpage

\graphAppendix{Good partition from a $J$-strip system}{alg:goodPartitionJStrip}
\input{coloringAppendix/algVIa.tex}
\clearpage

\graphAppendix{Good partition from a special $K_4$ strip system}{alg:goodPartitionSpecialK4}
\input{coloringAppendix/algVIb.tex}
\clearpage

\graphAppendix{Find a special $K_4$ system}{alg:findSpecialK4}
\input{coloringAppendix/algVII.tex}
\clearpage

\graphAppendix{Growing a $J$-strip}{alg:growingJStrip}
\noindent\input{coloringAppendix/algVIII.tex}
\clearpage

### 2020-09-15 paper/implementation.tex
Style fixes

To find an odd hole, we use a backtracking technique. We will enumerate all paths and holes and for each test if it is an odd hole. A partial solution to our problem is a path in $G$. To move forward from a partial solution, we append consecutively to its end all neighbors of current path's last vertex and continue recursively after each. When a current solution is an odd hole we return it. When we exhaust all possible paths from the current partial solution, we remove last vertex and continue. Also notice, that we can abandon ''paths'' that have chords.

@@

\subsubsection{Path enumerating optimizations}
Now let's turn our attention to enumerating all paths. This is a generalization of the problem of finding an odd hole, if we allow a path to have a single chord between the first and the last of its vertices if and only if the hole formed would be odd.

First of all, there are many methods for generating all possible paths to choose from. We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path (that is if all pairs of vertices next to each other are connected and that there are no chords), but this would be too slow and render our algorithm unusable.

@@

With those requirements defined a simplest algorithm would be to implement a sort of a "counter" with base of $|V(G)|$. In short: we take a path on a input, increment its last vertex until it is a neighbor of the vertex one before last. Then we check if generated sequence is a path (all vertices unique and no chords). If it is we return it and if we run out of vertices before a path is found, we increment one before last vertex until it is a neighbor of one vertex before it, set last vertex to first and continue the process. If still no path is found, we increment vertices closer to beginning of the path, until all a path is found or we check all candidates.

@@

Because of a good performance of our optimized algorithm for generating paths, we use it whenever possible. It can be easily modified to generate all possibly chordal paths or holes and therefore has much use in the CCLSV algorithm. For example, when searching for jewels we generate with it all possibly chordal paths of length 5 and for each check if it has required properties of a jewel. This proved to be much faster than generating vertices that don't have forbidden chords one by one. We use the same algorithm for generating starting vertices for a possible $\T_2$ and $\T_3$. Before optimizing path enumeration algorithm, all calls of $areUnique$ alone took abour 70\% of total running time of the CCLSV algorithm. After optimizing $areUnique$, path enumeration still took more than 50\% of total running time. After all optimizations it is almost unnoticable.

>>>>

To find an odd hole, we use a backtracking technique. We will enumerate all paths and holes and for each test if it is an odd hole. A partial solution to our problem is a path in $G$. To move forward from a partial solution, we append consecutively to its end all neighbors of current path's last vertex and continue recursively after each. When a current solution is an odd hole we return it. When we exhaust all possible paths from the current partial solution, we remove last vertex and continue.

@@

\subsubsection{Path enumerating optimizations}
Now let's turn our attention to enumerating all paths. This is a generalization of the problem of finding an odd hole, if we allow a path to have a single additional edge between the first and the last of its vertices if and only if the hole formed would be odd.

First of all, there are many methods for generating all possible paths to choose from. We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path (that is if all pairs of vertices next to each other are connected and that there are no other edges), but this would be too slow and render our algorithm unusable.

@@

With those requirements defined a simplest algorithm would be to implement a sort of a "counter" with base of $|V(G)|$. In short: we take a path on a input, increment its last vertex until it is a neighbor of the vertex one before last. Then we check if generated sequence is a path. If it is we return it and if we run out of vertices before a path is found, we increment one before last vertex until it is a neighbor of one vertex before it, set last vertex to first and continue the process. If still no path is found, we increment vertices closer to beginning of the path, until all a path is found or we check all candidates.

@@

Because of a good performance of our optimized algorithm for generating paths, we use it whenever possible. It can be easily modified to enumerate all ''paths'' that can have additional edges or to enumerate holes and therefore has much use in the CCLSV algorithm. For example, when searching for jewels we generate with it all ''paths'' with possible additional edges, of length 5 and for each check if it has required properties of a jewel. This proved to be much faster than generating vertices and checking their properties one by one. We use the same algorithm for generating starting vertices for a possible $\T_2$ and $\T_3$. Before optimizing path enumeration algorithm, all calls of $areUnique$ alone took abour 70\% of total running time of the CCLSV algorithm. After optimizing $areUnique$, path enumeration still took more than 50\% of total running time. After all optimizations it is almost unnoticable.

### 2020-09-15 paper/main.tex
Calculating \vartheta
experiments wip
Save!
Fixes KT
Plots and appendix
Much pogrress
Style fixes

\begin{abstract}
	TODOa
\end{abstract}

\listoftheorems[ignoreall,show={defn}]
\tableofcontents

@@

\chapter{Perfect Graphs}
\input{perfectGraphs.tex}
\input{coloringBergeGraphs.tex}

\chapter{Implementation}
\input{implementation.tex}

@@

\chapter{Perfect Graph Coloring algorithm}
TODO

@@

>>>>

\begin{abstract}
	Perfect graphs are a subject of intense study since their introduction in 1961. Only in 2001 a famous conjecture known as a strong perfect graph conjecture was proven to be true and in 2005 a polynomial method of determining if a graph is perfect was found. Since 1988 an algorithm is known for coloring perfect graphs, but it uses an ellipsoid method which is said to be complicated an impractical. As recently as in 2018 a polynomial algorithm for coloring perfect graphs without squares was published, that uses a combinatorial approach.

	In Chapter 1 we introduce perfect graphs and Berge graphs, give an overview of the strong perfect graph theorem and talk about an algorithm for polynomial perfect graph recognition. Chapter 2 is a study of the ellipsoid method of coloring perfect graphs. In Chapter 3 we present our implementation of algorithms from Chapters 1 and 2, along with notes on optimization and parallelisation. Appendix A is a overview of the recent algorithm for coloring square-free perfect graphs.
\end{abstract}

\listoftheorems[ignoreall,show={defn}]
\renewcommand{\listtheoremname}{List of algorithms}
\listoftheorems[ignoreall,show={alg}]
\tableofcontents

@@

\chapter{Perfect Graphs}
\input{perfectGraphs.tex}

\chapter{Coloring Perfect Graphs}
\input{coloringBergeGraphs.tex}

\chapter{Implementation}
\input{implementation.tex}
\input{experiments.tex}

@@

\input{appendA.tex}

@@

% \begin{figure}
% 	\input{tikzpictures/3dtest.tex}
% 	\caption{3d test}
% \end{figure}
